\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amssymb}



\begin{document}

\begin{center}
   \huge\textbf{Ahmed M Abdullahi}\\
   \small Louisville, KY\\
   \small $\mathbb{A}$* (502) 701-3239 $\bullet$ $\mathbb{R}$[regular] amabdu02@louisville.edu\\
   \small ahmedmurshid.github.io/my-site/ $\bullet$ $\mathbb{D}$ ahmed-abdullahi
\end{center}

\section*{Career Goal}
Contribute to innovative projects and collaborate with others for mutual growth

\section*{Education}
\textbf{J.B. Speed School of Engineering, University of Louisville} \hfill Louisville, KY\\
Bachelor of Arts in Computer Science \hfill Expected Dec 2024\\
GPA: 3.44

\section*{Experience}
\textbf{UPS} \hfill Louisville, KY\\
ISM CO-OP, ISM Intern \hfill May 2023 -- Present\\
Skills: C\#, PL/SQL, Oracle Database, Data Storage Technologies, Data Analytics, Data Visualization, Data Analysis.

\textbf{Spd-Speed Info Technology} \hfill United States\\
Student Help Desk IT \hfill Oct 2022 -- Jul 2023\\
Skills: Network Troubleshooting, Computer Hardware Troubleshooting, Communication.

\textbf{UofL Health} \hfill Louisville, KY\\
PRN Patient Access Registrar \hfill Feb 2022 -- Oct 2022

\section*{Projects}
\textbf{AI NP-Complete Problems: A Deep Dive into the Chinese Postman Problem} \hfill Python\\
Implemented a novel approach combining Genetic Algorithms (GA) and Wisdom of Crowds (WoC) to solve the Chinese Postman Problem. Developed a hybrid GA+WoC algorithm to find the shortest closed path that visits every edge of a graph.

\textbf{UPS - WTO Refresh - Toad Oracle Project} \hfill PL/SQL \& SQL\\
Used Toad for Oracle to develop and refresh complex PL/SQL procedures, functions, and SQL scripts for the WTO database systems.

\textbf{Meal Rater App} \hfill SQLite \& Java\\
Built an Android app in Java with SQLite for database management, allowing users to rate meals from various restaurants.\\
Github Link

\section*{Activities \& Honors}
\begin{itemize}
   \item HomeLab Ubuntu Server: Set up and maintain a home server using Ubuntu for personal projects and experimentation.
   \item Dean Scholar: Awarded for outstanding academic performance at the university.
   \item UofL Dean's List: Recognized for high academic achievement in 2020, 2022, 2023.
   \item Hackathon - Cardinal Impact Weekend: Participated and secured 1st place in the 2023 competition focused on innovative tech solutions.
\end{itemize}

\section*{Programs \& Volunteer Work}
\begin{itemize}
   \item Muhammad Ali Center Council of Students: Member from Aug 2016 -- May 2020, engaged in community service and leadership activities.
   \item Youth Leadership Fellowship: Completed a leadership development program in Aug 2020.
   \item Trio Upward Bounds: Volunteered in 2019 to support educational initiatives for high school students.
\end{itemize}

\end{document}o 